MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
replaced w/l with 1/0

```{r}

df[,W] <- as.character(df[,W])

for (i in 1:nrow(df)) {
  df[i,] <- as.character(ky[, i])
  if (df[i,"W"]="W") df[i,"W"]<- 1
  if (df[i,"W"]="L") df[i,"W"]<- 0
}

for (i in 1:(ncol(ky) - 1)){
  ky[, i] <- as.character(ky[, i])
  for (j in 1:nrow(ky)){
    if (ky[j, i] == "Strongly Agree") ky[j, i] <- 5
    if (ky[j, i] == "Agree") ky[j, i] <- 4
    if (ky[j, i] == "Neither Agree nor Disagree") ky[j, i] <- 3
    if (ky[j, i] == "Disagree") ky[j, i] <- 2
    if (ky[j, i] == "Strongly Disagree") ky[j, i] <- 1
  }
  ky[, i] <- as.numeric(ky[, i])
}

>>>>

```
### Home Advantage analysis
```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

for (i in 1:nrow(df)) {
  if (df[i,"W"]=="W") df[i,"W"]<- 1
  if (df[i,"W"]=="L") df[i,"W"]<- 0
}

df[,"W"] <- as.numeric(df[,"W"])
